Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-05 paper.tex
Remove fake TODO
added missing figure

Much research is currently being done to study how non-volatile and large
memory systems would change system design.  We see the need for a lightweight
tool to study such systems at scale with real workloads.  The first step
towards building such a tool is to study the scalability of existing memory
management systems.  We find that in most cases, Linux kernel memory management
scales well with large amounts of physical memory. However, workloads that
allocated many virtual memory areas can accumulate significant memory and
computational overhead due to kernel metadata.     Furthermore, in certain
situations, transparent hugepages can nullify the benefits from better TLB
reaches by inducing memory pressure earlier, even for workloads that would
otherwise not experience it.  Finally, we see that the 99.99-th percentile of
disk latency during swapping can account for over 70\% of runtime for the
workloads we tested.

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

@@

Figure (TODO) shows the total number of jiffies spent running kswapd as the
number of operations performed increases. Notice that one jiffy corresponds to
10ms of runtime.

>>>>

Much research is currently being done to study how non-volatile and large
memory systems would change system design.  We see the need for a lightweight
tool to study such systems at scale with real workloads.  The first step
towards building such a tool is to study the scalability of existing memory
management systems.  We find that in most cases, Linux kernel memory management
scales well with large amounts of physical memory. However, workloads that
allocated many virtual memory areas can accumulate significant memory and
computational overhead due to kernel metadata.     Furthermore, in certain
situations, transparent hugepages can nullify the benefits from better TLB
reaches by inducing memory pressure earlier, even for workloads that would
otherwise not experience it.  Finally, we see that the tail
swapping latencies can account for over a majority of runtime for the
workloads we tested.

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks.}
    \label{fig:vm_area_struct_count}
\end{figure}

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/kswapd_jiffies}
    \caption{Number of jiffies spent by kswapd.\label{fig:kswapd_jiffies}}
\end{figure}

@@

Figure \ref{fig:kswapd_jiffies} shows the total number of jiffies spent running kswapd as the
number of operations performed increases. Notice that one jiffy corresponds to
10ms of runtime.
